О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Remove a redundant lemma
Fix a lemma formulation

\begin{lemma}
	\cite[Corollary 1]{our-vmmsh-2018}
	\label{lem:max_points_on_line}
	Let $M\in\mathfrak{M}(2,n)$, $\operatorname{diam} M = d$.
	Then there is no straight line which contains more than $(d+3)/2$ points of $M$.
\end{lemma}

@@

\begin{lemma}
	\label{lem:intervals_cross}
	If \textbf{open} line segments $M_1 M_2$ and $M_3 M_4$ does not intersect,
	$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains not more than 4 points.
\end{lemma}

>>>>

@@

\begin{lemma}
	\label{lem:intervals_cross}
	If \textbf{open} line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains not more than 4 points.
\end{lemma}
